---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geniusfetchR

<!-- badges: start -->
<!-- badges: end -->

The goal of geniusfetchR is to  to assist researchers who want to build lyrical datasets for analysis with a collection of helper functions for fetching song lyrics, album tracklists, and artist discographies from Genius or other lyrics websites. It was created as a workaround to several problems encountered in the geniusr package.


## Installation

You can install the development version of geniusfetchR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ajholt25/R-Programming")
```

## Examples


### Fetch album lyrics for a specific artist and album:
```{r example-album}
library(geniusfetchR)
library(dplyr)
library(rvest)
library(stringr)
library(xml2)
genius_album_fetcher("Fleetwood Mac", "Rumours")
```

### Fetch lyrics for multiple artists and albums:
```{r example-multi-artist}
library(geniusfetchR)
library(dplyr)
library(rvest)
library(stringr)
library(xml2)
artists <- c("Fleetwood Mac", "Fleetwood Mac", "The Rolling Stones", "The Rolling Stones")
albums <- c("Rumours", "Tusk", "Let It Bleed", "Sticky Fingers")
genius_album_fetcher(artists, albums)
```

### Fetch lyrics for a specific song:
```{r example-song}
library(geniusfetchR)
library(dplyr)
library(rvest)
library(stringr)
library(xml2)
genius_song_fetcher("The Rolling Stones", "Paint It Black")
```

